---
title: CSC115 Ch5 HW Help
author: Natalie Lenberger
date: '2017-09-28'
slug: csc115-ch5-hw-help
categories:
  - HW Help
  - R
tags:
  - CSC115
  - HW Help
---

```{r include=FALSE}
library(TurtleGraphics)
knitr::opts_chunk$set(fig.align = "center", out.width = "80%")
```


Before beginning this assignment we must first take care of a couple housekeeping things in R. 

First you must load the package `TurtleGraphics`
```{r eval=FALSE}
library(TurtleGraphics)
```

## Exercise 1

#### The Problem 

Using the `TurtleGraphics` funciton write a function called 'turtle_gon()' that draws a regular polygon. The user should be able to specifiy the side-length and the number of sides. Usig your function draw a polygon with 12 sides, each having a length of 15 units. Make sure the polygon does not stray outside of the turtle's field. 

#### Hints to get you to the soulution 

First remind yourself on how to right a function using `function()`. An example may be:
```{r, echo=TRUE}
exampleFunc <- function(n="How are you?"){
  cat(n)
}
```

```{r}
exampleFunc() ## Testing the Function
```

It works!

Next think about the parameters that may need to be used in your function allowing users to change the side-length and the number of sides in their polygon.

For the body of the function you may want to consider using a for loop.  An example of this is:
```{r, fig.keep="last", echo=TRUE, fig.cap="Square with equal sides of 35 units"}
turtle_init()  ##Always remember to initialize your turtle!
for(i in 1:4){
  turtle_forward(dist=35)
  turtle_right(angle=90)
}
```

This gives us a square with sides equal to 35 units!


Thinking about what to do if we don't know how many sides or their lengths:

* Instead of numbers, there will be variables.
* There may be a small formula for determining the size of the angle.


Once you have your function made, make sure you think about what to do in order to keep the polygon within the field of the turtle!


## Exercise 2

#### The problem
Write a function called `turtle_star()` where the user can specify the following:
 
  * number of rays in a star
  * length of rays
  * color of rays
  * line-type of rays
  * line-width of rays
  
#### Hints to get you to the soulution
For looping will probably still be beneficial here!

Think about variables that will remain the same throughout the entire loop. Shouldn't those go before the for loop?

When writing the function, it may help to map out each movement you are telling the turtle to do. 


## Exercise 3

#### The problem
Write a function called `turtle_rstar()` in which the lengths are not determined by the user, but instead vary randomly from 5 to 25 units.

#### Hints to get you to the solution
Wasn't there a function we read about in chapter 5 that pulled randomly from a specified set of numbers?

What if we used that function: `runif()`?

If I wanted two random numbers between 2 and 12 I could use the following code:
```{r}
runif(2,2,12)  
```

Maybe we could try putting that into our function?
Try it out!!!


## Exercise 4

#### The problem
Make a new star function called `turtle_rstarColors()` that will behave like `turtle_rstar()`, except instead of the color being specified by the user, the ray-color should vary from one ray to another.

#### Hints to get you to the solution
Recall a function we looked at in a previous chapter, `sample()`. Can't this function randomly select values? What if we used this function to randomly assign a color to each ray in the star?




